% Copyright 2018-2019 Emir Turkes
%
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%     http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.

% Section title
\cvsection{Experience}
\vspace*{0.35cm}

% Content
\begin{cventries}

    \cventry{\href{https://www.pathology.columbia.edu/profile/karen-e-duff-phd}
        {Columbia University Medical Center \textit{under Karen Duff, PhD}}}
    {Lab Technician}
    {New York, NY}
    {February 2019 - Present}
    {\begin{cvitems}
        \item{Carry out \MYhref[awesome]{https://github.com/eturkes/E-I-physiology}
            {bioinformatics analysis} of multiomics data with the goal of uncovering the
            pathology of Alzheimer's disease and related tauopathies.\vspace*{0.1cm}}
        \item{Develop machine-learning driven methodologies in pharmacoepidemiology,
            natural language processing, and biochemical pathway analysis for the
            generation of testable hypotheses for drug discovery.}
    \end{cvitems}}
    \vspace*{0.2cm}

    \cventry{\href{https://www.phenovance.com}
        {Phenovance LLC \textit{under Toshihiro Endo, PhD}}}
    {Graduate Student}
    {Chiba, Japan}
    {September 2016 - March 2018}
    {\begin{cvitems}
        \item{\MYhref[awesome]
            {https://drive.google.com/file/d/1jhGISUcJ92PAX5JeoeydUG91Vgol1ftz/view?usp=sharing}
            {Wrote} and \MYhref[awesome]
            {https://drive.google.com/file/d/1DReIxHOwp1rkpVX2zOcl-vvD8Mrh-gZ9/view?usp=sharing}
            {defended} master's thesis on the development of new software and
            experimental paradigms for Intellicage, an automated home cage system for
            reproducible animal behavior research. Phenotyping of a novel oxytocin
            receptor knockout model of autism did not reveal significant differences
            from control but suggests directions for future paradigms.\vspace*{0.1cm}}
        \item{Currently working on \MYhref[awesome]
            {https://github.com/eturkes/pymice-tools}{PyMICE Tools}, an extension to the
            PyMICE Python library for Intellicage that adds automated \MYhref[awesome]
            {https://github.com/eturkes/pymice-analyzer}{pipeline manipulation}, an
            \MYhref[awesome]{https://github.com/eturkes/pymice-modules}{API} for
            open-source development, and an \MYhref[awesome]
            {https://github.com/eturkes/pymice-server}{interface} for HPC cluster
            usage.\vspace*{0.1cm}}
        \item{Helped maintain and prep mouse colonies, particularly implantation of RFID
            tags and infusion pumps, drug administration, and brain dissection/isolation
            for epigenome and transcriptome analysis.\vspace*{0.1cm}}
        \item{Master's work funded under the Rotary Yoneyama \MYhref[awesome]
            {https://drive.google.com/file/d/1if78hZlVqVEMfAY14bLCkvQsiyt0pdkU/view?usp=sharing}
            {Scholarship}.}
    \end{cvitems}}
    \vspace*{0.2cm}
    
    \cventry{\href{http://sites.bu.edu/guentherlab}
        {Boston University Speech Lab \textit{under Frank Guenther, PhD, MS}}}
    {Research Assistant}
    {Boston, MA}
    {June 2015 - February 2016}
    {\begin{cvitems}
        \item{Presented a first author \MYhref[awesome]
            {https://drive.google.com/file/d/1GY3jYHsbGaiG6U23mudORFMrKd_H6WJn/view?usp=sharing}
            {poster} at NeuroHAM on Human Connectome Project rs-fcMRI analyses that
            suggest multiple changes to the DIVA model of speech 
            production.\vspace*{0.1cm}}
        \item{Created MATLAB scripts that automate the generation of formatted
            functional \MYhref[awesome]
            {https://drive.google.com/file/d/1mpDEeY-ioQqpYMHYav5BsmWH3nSTK6Io/view?usp=sharing}
            {connectivity maps} that have since been compiled into a \MYhref[awesome]
            {https://bit.ly/2Pn5ySL}{book} describing speech motor control. Began
            conversion of scripts into a complete \MYhref[awesome]
            {https://drive.google.com/file/d/1jxKIMhd4fFk7Kuw5xKsTZi-xL1VaNFTu/view?usp=sharing}
            {MATLAB toolbox}.\vspace*{0.1cm}}
        \item{Assisted in various other fMRI and tractography analyses, particularly
            with autistic and stuttering patients.\vspace*{0.1cm}}
        \item{Contributed \MYhref[awesome]
            {https://drive.google.com/file/d/1Ja6C8LZ03-h8wgXsYvfLqmOcwIxX_Uic/view?usp=sharing}
            {documentation} that greatly assisted new and existing members of the lab.}
    \end{cvitems}}
    \vspace*{0.2cm}
    
    \cventry{\href{https://drive.google.com/file/d/1OB2jnfXYUQhHXx6eUszbmHep6D2VY0j1/view?usp=sharing}
        {Boston University NE204 \textit{under Mark Kramer, PhD}}}
    {Learning Assistant \textnormal{\small{\textit{(volunteer)}}}}
    {Boston, MA}
    {January 2015 - May 2015}
    {\begin{cvitems}
        \item{Provided instruction on the use of Matlab for \MYhref[awesome]
            {https://youtu.be/uE-xM6tPxWQ}{NE204}: Intro to Computational Models of
            Brain and Behavior.}
    \end{cvitems}}
    \vspace*{0.2cm}
    
    \cventry{\href{http://www.shoreneurology.com}
        {Shore Neurology PA \textit{under Gerald Ferencz, MD}}}
    {Research Assistant \textnormal{\small{\textit{(volunteer)}}}}
    {Toms River, NJ}
    {May 2013 - August 2013}
    {\begin{cvitems}
        \item{Created and analyzed the results of a \MYhref[awesome]
            {https://drive.google.com/file/d/1VDZvp7pQQrq2qAgaSJuokn2wpzV0uqvj/view?usp=sharing}
            {survey} to address the needs of caregivers within Ocean County,
            NJ.\vspace*{0.1cm}}
        \item{Helped coordinate Phase II, III, and IV clinical trials for treatment of
            neurological disease.}
    \end{cvitems}}
    \vspace*{0.2cm}
    
\vspace*{-0.2cm}
\end{cventries}
